\printbibliography[heading=bibintoc]
\begin{thebibliography}{X}
	
	\bibitem{ir} Luk, R. W. P. (2022). "Why is information retrieval a scientific discipline?". Foundations of Science.
	
	\bibitem{hugging_face} Página oficial de Hugging Face
	
	\url{https://huggingface.co/}
	
	\bibitem{hugging_face_hub} Documentación de Hugging Face Hub
	
	\url{https://huggingface.co/docs/hub/index}
	
	\bibitem{nlp} Vásquez, Augusto Cortez; Huerta, Hugo Vega; Quispe, Jaime Pariona; Huayna, Ana Maria (2009). «Procesamiento de lenguaje natural». Revista de investigación de Sistemas e Informática
	
	\bibitem{bert} Devlin, Jacob; Chang, Ming-Wei; Lee, Kenton; Toutanova, Kristina (11 October 2018). "BERT: Pre-training of Deep Bidirectional Transformers for Language Understanding"
	
   \bibitem{bert_award} "Best Paper Awards". NAACL. 2019
   
   \url{https://naacl2019.org/blog/best-papers/}
   
   \bibitem{gpt} Dale, R. (2021). GPT-3: What’s it good for?. Natural Language Engineering
   
	\bibitem{nsir} Radev, D. R., Qi, H., Wu, H., & Fan, W. (2002, May). Evaluating Web-based Question Answering Systems. In LREC.
	
	\bibitem{s2qa} Xu, S., Campagna, G., Li, J., & Lam, M. S. (2020, October). Schema2qa: High-quality and low-cost q&a agents for the structured web. In Proceedings of the 29th ACM International Conference on Information & Knowledge Management 
	
	\bibitem{smartq} Lin, Y., & Shen, H. (2017). SmartQ: A question and answer system for supplying high-quality and trustworthy answers. IEEE Transactions on Big Data
	
	\bibitem{apirest} Documentación de Integración de Aplicaciones de Amazon
	
	
	\url{https://aws.amazon.com/es/what-is/api/#:~:text=API%20significa%20%E2%80%9Cinterfaz%20de%20programaci%C3%B3n,de%20servicio%20entre%20dos%20aplicaciones.}


	\bibitem{frontend_vs_backend} Qué es Frontend y Backend: diferencias y características - Platzi
	
	\url{https://platzi.com/blog/que-es-frontend-y-backend/}
	
	\bibitem{encuesta2022} Encuesta de StackOverflow 2022
	
	
	\url{https://survey.stackoverflow.co/2022/#most-popular-technologies-webframe}
	
	\bibitem{react} Aggarwal, S. (2018). Modern web-development using reactjs. International Journal of Recent Research Aspects
	
	\bibitem{angular} Documentación oficial de Angular
	
\url{https://angular.io/guide/what-is-angular}
	
\bibitem{vue} Documentación oficial de Vue


\url{https://vuejs.org/guide/introduction.html}


\bibitem{jquery} Página oficial de JQuery

\url{https://jquery.com/}

\bibitem{nuxt} Documentación oficial de Nuxt 3

\url{https://v3.nuxtjs.org/guide/concepts/auto-imports}

\bibitem{bootstrap} Gaikwad, S. S., & Adkar, P. R. A. T. I. B. H. A. (2019). A review paper on bootstrap framework. IRE Journals

\bibitem{tailwind} Página oficial de Tailwind CSS

\url{https://tailwindcss.com/}

\bibitem{node} Cantelon, M., Harter, M., Holowaychuk, T. J., & Rajlich, N. (2014). Node. js in Action

\bibitem{express} Archer, R. (2016). Express. js: Web App Development With Node. js Framework.

\bibitem{django} Forcier, J., Bissex, P., & Chun, W. J. (2008). Python web development with Django. Addison-Wesley Professional.

\bibitem{flask} Documentación oficial de Flask

\url{https://flask.palletsprojects.com/en/2.2.x/}

\bibitem{fastapi} Página oficial de Fast Api

\url{https://fastapi.tiangolo.com/}

\bibitem{golang} Documentación oficial de Go

\url{https://go.dev/doc/}

\bibitem{buffalo} Página oficial de Buffalo
 
\url{https://gobuffalo.io/en/} 

\bibitem{gorilla} Página oficial de Gorilla

\url{http://www.gorillatoolkit.org/}

\bibitem{gin} Documentación oficial de Gin

\url{https://gin-gonic.com/docs/}

\bibitem{bd_relational} Codd, E. F. (1970). A relational model of data for large shared data banks. Communications of the ACM,

\bibitem{codd_turing}  Edgar F. Codd - A.M. Turing Award Winner

\url{http://amturing.acm.org/award_winners/codd_1000892.cfm}

\bibitem{nosql} NoSQL, documentación en español de AWS

\url{https://aws.amazon.com/es/nosql/}

\bibitem{postgres} Página oficial de PostgreSQL

\url{https://www.postgresql.org/}

\bibitem{redis} Página oficial de Redis

\url{https://redis.io/}

\bibitem{jwt} \url{https://jwt.io/}

\bibitem{docker} Página oficial de Docker

\url{https://www.docker.com/}

\bibitem{docker_docs} Documentación oficial de Docker

\url{https://docs.docker.com/get-started/}

\bibitem{orm} What is Object/Relational Mapping?. Hibernate Overview. JBOSS Hibernate. Retrieved 27 January 2022.

\bibitem{gorm} Documentación oficial de Gorm

\url{https://gorm.io/docs/}
	
\end{thebibliography}